Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 conclusions.tex
next round of comments
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@977 ccdd05d5-56c1-461a-bf98-85f6876523b4

The algorithm we described has no intrinsic latency.  However, there are
fundamental and practical latencies associated with the analysis and detection
procedure. For example, the \LIGO{} detectors, data acquisition is synchronized
to a 1/(16~Hz) cadence, introducing an up-front latency~\cite{CITE_CDS}. Data
aggregation from
the observatories will travel over various networks, each capable of high
bandwith but perhaps only modest latency.  This could amount to a similar
latency of $\sim$100 ms.  Lastly, unless a real-time infrastructure is adopted
post data acquisition, it is likely that there will be an inherent latency
introduced by such infrastructure.  We have shown a prototype implementation
of \lloid{} using \gstlal\ that is capable of order seconds latency. Based
on our experience, significant work would have to be done in order to improve
upon this number, for example, more tightly integrating analysis and data
acquisition. This should be considered for third-generation detector design.

>>>>

The algorithm we described has no intrinsic latency.  However, there are
fundamental and practical latencies associated with the analysis and detection
procedure. For example, the \LIGO{} detectors, data acquisition is synchronized
to a 1/(16~Hz) cadence, introducing an up-front latency~\cite{Bork2001}. Data
aggregation from the observatories will travel over various networks, each
capable of high bandwith but perhaps only modest latency.  This could amount to
a similar latency of $\sim$100 ms.  Lastly, unless a real-time infrastructure
is adopted post data acquisition, it is likely that there will be an inherent
latency introduced by such infrastructure.  We have shown a prototype
implementation of \lloid{} using the open source signal processing software
\gstreamer\ and \gstlal. Significant work would have to be done in order to
improve upon the latency capability of our implementation, for example, more
tightly integrating analysis and data acquisition. This should be considered
for third-generation detector design.
